%! Author = Luke Briggs
%! Date = 2021/07/09

\documentclass{article}
\usepackage[comma]{natbib}
\usepackage[colorlinks=true]{hyperref}
\usepackage{listings}
\usepackage[margin=2cm]{geometry}
\usepackage[UKenglish]{isodate}
\usepackage{xcolor}
\usepackage{bibentry}
\bibliographystyle{newcastle}
\definecolor{codebg}{RGB}{246, 245, 244}
\lstdefinestyle{mystyle}{
    basicstyle=\linespread{1.1}\ttfamily\footnotesize,
    backgroundcolor=\color{codebg}
}
\lstset{showstringspaces=false, style=mystyle}

\begin{document}
\nobibliography{bibliography}
\title{newcastle-bst: Harvard referencing style as recommended by Newcastle University}
\author{Maintainer: Luke Briggs}
\date{Package v1.1 - \printdate{2021-07-10}}
\maketitle

\section{Introduction}
This package provides a \href{https://ctan.org/pkg/BibTeX}{BibTeX} style to format reference lists in the \href{https://libguides.ncl.ac.uk/managing/harvard}{Harvard at Newcastle} style recommended by Newcastle University. 
It should be used alongside \href{https://ctan.org/pkg/natbib}{natbib} for citations.

\subsection{Installation}
The required style file is available from \href{https://github.com/LukeBriggsDev/Newcastle-BibTeX}{GitHub} and \href{https://ctan.org/pkg/newcastle-bst}{CTAN}. 
You can use the style by copying it into your working directory containing your `.tex` file. 
You can also add it to your bst directory in your tex path to use it without having to copy it over each time.

\subsection{Using the style}
To use the style include this in your preamble:
\begin{lstlisting}[language=tex]
\usepackage{natbib}
\usepackage[UKenglish]{isodate}
\bibliographystyle{newcastle}
\end{lstlisting}

Also remember to specify your `.bib` file at the end of the document:
\begin{lstlisting}[language=tex]
\bibliography{file}
\end{lstlisting}

This style is designed to be used alongside \href{https://ctan.org/pkg/natbib}{natbib} and it is the commands from this package that you should use when citing:
\begin{itemize}
    \item \lstinline!\citet{key} ==>>                 Jones et al. (1990)!
    \item \lstinline!\citet*{key} ==>>                Jones, Baker, and Smith (1990)!
    \item \lstinline!\citep{key} ==>>                 (Jones et al., 1990)!
    \item \lstinline!\citep*{key} ==>>                (Jones, Baker, and Smith, 1990)!
    \item \lstinline!\citep[chap. 2]{key} ==>>        (Jones et al., 1990, chap. 2)!
    \item \lstinline!\citep[e.g.][]{key} ==>>         (e.g. Jones et al., 1990)!
    \item \lstinline!\citep[e.g.][p. 32]{key} ==>>   (e.g. Jones et al., 1990, p. 32)!
    \item \lstinline!\citeauthor{key} ==>>            Jones et al.!
    \item \lstinline!\citeauthor*{key} ==>>           Jones, Baker, and Smith!
    \item \lstinline!\citeyear{key} ==>>              1990!
\end{itemize}

\section{Examples}

The easiest way to create .bib files for this style is through exporting entries from a reference manager such as \href{https://www.mendeley.com/}{Mendeley}.
However, some parts are not available through this (such as titleaddon for computer programs).
If you notice any discrepancies between generated references and the recommended styles then please raise this on \href{https://github.com/LukeBriggsDev/Newcastle-BibTeX/issues}{GitHub}

\subsection{Books and book chapters}
\subsubsection*{Book with author(s)}


\bibentry{Ammann2016}

\begin{lstlisting}
@book{Ammann2016,
address = {Cambridge, United Kingdom},
author = {Ammann, Paul and Offutt, Jeff},
doi = {10.1017/9781316771273},
edition = {2},
pages = {26},
publisher = {Cambridge University Press},
title = {{Introduction to Software Testing}},
year = {2016}
}
\end{lstlisting}

\subsubsection*{Book with editor(s) instead of authors}

\bibentry{rothman.etal2008me}

\begin{lstlisting}
@book{rothman.etal2008me,
editor = {Kenneth J. Rothman and Sander Greenland and Timothy L. Lash},
year = {2008},
title = {Modern Epidemiology},
edition = {3},
address = {Philadelphia, Pa.},
publisher = {Lippincott Williams \& Wilkins}
}
\end{lstlisting}

\subsubsection*{Book known by its title}

\bibentry{bnf2020}

\begin{lstlisting}
@book{bnf2020,
year = {2020},
title = {{British National Formulary}},
edition = {79},
address = {London},
publisher = {Pharmaceutical Press}
}
\end{lstlisting}

\subsubsection*{One chapter from a collection (by different authors) in an edited book}

Cunningham, W. (2008) ‘Ward Cunningham, inventor of Wiki, inventor of Fit, coinventor of eXtreme Programming.’In R.C. Martin, (ed.)Clean Code: A Handbook of Agile Software Craftsmanship. Boston, MA: Pearson Education,Inc, p. 11.

\begin{lstlisting}
@incollection{Cunningham2008,
address = {Boston, MA},
author = {Cunningham, Ward},
booktitle = {Clean Code: A Handbook of Agile Software Craftsmanship},
editor = {Martin, Robert C.},
isbn = {978-0-13-235088-4},
pages = {11},
publisher = {Pearson Education, Inc},
title = {{Ward Cunningham, inventor of Wiki, inventor of Fit, coinventor of eXtreme Programming.}},
year = {2008}
}
\end{lstlisting}

\subsection{Articles and periodicals}
\subsubsection{Journal article}

Stevens,  W.P.,  Myers,  G.J.  and  Constantine,  L.L.  (1999)  ‘Structured  design’.IBM Systems Journal,  38(2),  pp.231–256.  doi:  10.1147/sj.382.0231.4

\begin{lstlisting}
@article{Stevens1999,
author = {Stevens, W. P. and Myers, G. J. and Constantine, L. L.},
doi = {10.1147/sj.382.0231},
issn = {00188670},
journal = {IBM Systems Journal},
number = {2},
pages = {231--256},
title = {{Structured design}},
volume = {38},
year = {1999}
}
\end{lstlisting}

\subsubsection{Newspaper article}

Haurant, S. (2004) ‘Britain’s borrowing hits£1 trillion’.The Guardian, 29 July, p. 16c.

\begin{lstlisting}
@article{haurant2004bbh,
author = {Haurant, S.},
year = {2004},
title = {Britain's Borrowing Hits \pounds 1 Trillion},
journal = {The {Guardian}},
volume = {29 July},
pages = {16c}
}
\end{lstlisting}

\subsection{Digital media}
\subsubsection{Website/webpage}

\bibentry{Letouzey2016}

\begin{lstlisting}
@misc{Letouzey2016,
abstract = {What is Technical Debt? Where does it comes from?},
author = {Letouzey, Jean Louis and Whelan, Declan},
booktitle = {Agile Alliance},
pages = {4},
title = {{Introduction to the Technical Debt Concept}},
url = {https://www.agilealliance.org/wp-content/uploads/2016/05/
        IntroductiontotheTechnicalDebtConcept-V-02.pdf},
urldate = {2020-01-02},
year = {2016}
}
\end{lstlisting}

\subsubsection{Computer Program}

\bibentry{Briggs2021}

\begin{lstlisting}
@misc{Briggs2021,
author = {Briggs, Luke},
title = {{Pepys}},
titleaddon = {(v.1) [computer program]},
url = {https://lukebriggs.dev/pepys},
year = {2021},
}
\end{lstlisting}

\clearpage

\end{document}

